Testing Quasar Unification with Clumpy Wind Models

### 2015-11-10 paper.tex
added hubeny refs

We use the same atomic data as described by LK02 and since updated by H13 and M15, 
with the addition of direct ionization data from \cite{dere2007}. 
Photoionization cross-sections are from \textsc{Topbase} \citep{cunto1993} and  \cite{vfky}.
Dielectronic and radiative recombination rate coefficients are taken from 
the \textsc{Chianti} database version 7.0 \citep{dere1997,landi2012}.
We use ground state recombination rates from \cite{badnell2006} where available,
and otherwise default to calculating recombination rates from the Milne
relation. Free-free Gaunt factors are from \cite{sutherland1998}.

@@

BALQSOs and quasars generally possess very similar emission line properties 
\citep[e.g.][]{weymann1991,reichard2003}. 
Clearly, the variation with inclination in our models is far greater than 
than the variation between, and standard deviation within, quasar and BALQSO samples.  
This presents a challenge to our model, as well as the geometric unification picture in general.
One obvious potential solution is to hypothesize a more isotropic distribution 
for the emergent condition than predicted by a classical thin disc. 
General relativistic effects -- specifically, light bending
and relativistic beaming -- can cause 
the accretion disc SED to become more isotropic \citep[e.g.][]{zhang1997,munozdarias2013}. 
However, we have verified using AGNSPEC (REFs to Hubeny)
that this effect is small in the UV and optical wavelength regimes, 
and the disc is still anisotropic.

>>>>

We use the same atomic data as described by LK02 and since updated by H13 and M15, 
with the addition of direct (collisional) ionization and recombination
data from \cite{dere2007}. 
Photoionization cross-sections are from \textsc{Topbase} \citep{cunto1993} and \cite{vfky}.
%Dielectronic and 
Radiative recombination rate coefficients are taken from 
the \textsc{Chianti} database version 7.0 \citep{dere1997,landi2012}.
We use ground state recombination rates from \cite{badnell2006} where available,
and otherwise default to calculating recombination rates from the Milne
relation. Free-free Gaunt factors are from \cite{sutherland1998}.

@@

BALQSOs and quasars generally possess very similar emission line properties 
\citep[e.g.][]{weymann1991,reichard2003}. 
Clearly, the variation with inclination in our models is far greater than 
than the variation between, and standard deviation within, quasar and BALQSO samples.  
This presents a challenge to our model, as well as the geometric unification picture in general.
One obvious potential solution is to hypothesize a more isotropic distribution 
for the emergent condition than predicted by a classical thin disc. 
General relativistic effects -- specifically, light bending
and relativistic beaming -- can cause 
the accretion disc SED to become more isotropic \citep[e.g.][]{zhang1997,munozdarias2013}. 
However, we have verified using AGNSPEC \citep{hubeny2000,hubeny2001,hubenyhubeny1997}
that this effect is small in the UV and optical wavelength regimes, 
and the disc is still anisotropic.
